### 2022-05-30 chapters/04-chapter-4.tex
txs auto checkin

\subsubsection{Kasus SE1}
Dari gambar \ref{result_cpu_8} dan \ref{result_mem_8} terlihat bahwa \textit{engine} menggunakan \textit{resource} CPU sebanyak 0.046 \textit{core} dan Memory sebanyak 152.71 MiB.

>>>>

\subsubsection{Kasus SE1}
Dari gambar \ref{result_cpu_8} dan \ref{result_mem_8} terlihat bahwa \textit{engine} menggunakan \textit{resource} CPU sebanyak 0.075 \textit{core} dan Memory sebanyak 168.8 MiB.
